\section{The division meeting}

\subsection{Summons}
Summons for the division meeting consists of a proposed agenda. The proposed agenda shall be proclaimed at the division's official notice board. 

The division's official notice board must be located in Basen. 

\subsubsection{Proposed agenda}
The proposed agenda must contain the following: 

\begin{itemize}  
  \item Date, time and place for the meeting
  \item Opening of the meeting
  \item Election of chairman
  \item Election of secretary
  \item Election of two adjusters as well as tellers
  \item Previous minutes of the meeting
  \item Due proclamation of the meeting
  \item Rules of order
  \item Co-option
  \item Messages 
  \item Potential reports from student division committees 
  \item Potential year and audit reports 
  \item Potential elections
  \item Proposals from the board
  \item Member proposals
  \item Other questions 
\end{itemize}
\subsection{Location}
The division meeting must be held at Chalmers.

% \subsection{Rules of order}
% \subsubsection{Requesting the floor}
% The floor is requested by raising of a hand. The floor is given out in turns by the chairman of the meeting. 
 
% \subsubsection{Reply}
% If an address concerns a person, they have the right to reply of at most one minute. The reply must be directly connected with the address. A counterreply of at most one minute can be granted. Counter-counterreply is never granted. 

% \subsubsection{Point of order}
% A point of order breaks a debate in a factual matter and must be resolved before the debate continues. 

% \subsubsection{Motion for the previous question}
% Moving the previous question is treated as a point of order. If the motion for the previous question is approved, the chairman will review the list of speakers. After this point only those on the list may take the floor and no new requests for the floor may be made. 
% Repealing the motion for the previous question is also treated as a point of order. 

% \subsubsection{Proposals}
% Proposals are made both verbally and in writing to the chairman. 
% \subsubsection{Reservation}
% Reservation to a decision made by the meeting must be announced verbally in direct association to the decision and in writing within 24 hours after the meeting. 

% \subsubsection{Recess}
% A motion to recess is treated as a point of order. If the motion to recess is approved the duration of the recess must be set. 

\subsection{Speakers' council}
\subsubsection{Members}
The speakers' council consists of a speaker, a deputy speaker and a secretary.
\subsubsection{Task}
The tast of the speakers' council is to summon the division meeting in accordance with 4.2 in the constitution. The speaker is the chairman of the division meeting. The deputy speaker takes on the role of speaker in their absence. 

\subsubsection{Election}
The speaker, deputy speaker and secretary are elected by the division meeting. 

\subsubsection{Term}
The term is the same as the fiscal year. 

\subsubsection{Decisions made by the speakers' council}
The decisions of the speakers' council are taken by the speaker. This right is taken over by the deputy speaker in case the speaker is unable to perform their duties.

\subsection{Member proposals} 
A member proposal that is on the agenda must be raised and presented by the proposer or someone else at the meeting with the permission to propose, otherwise the member proposal falls. Further the board of the division must present their statement regarding the member proposal, after which general debate follows.  

\newpage
